---
title: "What the package does"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{What the package does}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753ehunt0108)

```

#Introduction

## This packages contains several functions that produce various statistical graphs, and a data set from the textbook.

#Myncurve Function

```{r}
myncurve(mu=10, sigma = 4, a = 6)
```
This function returns a plot of a normal curve and shows the probability that data is between certain parameters.

# Myboot2 function 

```{r}
set.seed(35); sam<-round(rnorm(30,mean=20,sd=3),3)
myboot2(iter=1000,x=sam, fun="mean",alpha=0.05,xlab="mean",cx=1.5)
```

This function returns a histogram, and a list containing the mean, confidence interval, and the data set of the sample.


# MyCLT function

```{r}
myclt(n=10,iter=10000,a=5,b=10)
```

This function returns a histogram showing the sum of uniform distributions given a sample size, iterations, and an upper bound and lower bound. 

#MyMLNorm function
```{r}
mymlnorm(x=c(10,12,13,15,12,11,10),mu=seq(10,15,length=1000), sig=seq(0.1,4,length=1000),lwd=2,labcex=1)
```

This function returns contour plot showing the mean and variance for the normal distribution max likelihood. 

